Investigating social change during cultural contact period using geometric morphometry of pottery shapes from Iron Age northeastern Taiwan

### 2020-01-31 analysis/paper/scraps.Rmd
combine two metric data tables

```{r metricCVstest-post-chi, eval=FALSE}
#-----------------------------------CV test for post-e and ch-con pair
kiwulan_pottery_metrics_cvs_plot_cv_test_asym_post_chi <-
  kwl_p_metrics_long_post_chi %>%
  nest(-variable) %>%  # or nest(period, value) %>%
  mutate(asymptotic_test = map(data, # change from mslr_test to asymptotic_test
                               ~bind_cols(asymptotic_test (
                                 .x$value,
                                 .x$period)))) %>%
  unnest(asymptotic_test)
# compute CV
kwl_p_cvs_pre_post <-
  kwl_p_metrics_long_post_chi %>%
  group_by(period, variable) %>%
  summarise(cvs = raster::cv(value, na.rm = TRUE))
# join p-values to CVs
kwl_p_cvs_and_pvalues_post_chi <-
  kwl_p_cvs_pre_post %>%
  left_join(kiwulan_pottery_metrics_cvs_plot_cv_test_asym_post_chi) %>%
  mutate(significant = ifelse(p_value <= 0.05, 'yes', 'no')) %>%
  mutate(variable = factor(variable, ordered = TRUE)) %>%
  arrange(variable)
# making table for CV
kwl_p_cvs_table_post_chi <-
  kwl_p_cvs_and_pvalues_post_chi %>%
  select(-data, -significant) %>%
  pivot_wider(names_from = period, values_from = cvs) %>%
  mutate(variable = factor(variable, levels = c("Rim thickness (mm)",
                                                "Neck thickness (mm)",
                                                "Body thickness (mm)",
                                                "Ratio of Rim/Body thickness",
                                                "Rim diameter (mm)",
                                                "Neck diameter (mm)",
                                                "Body diameter (mm)",
                                                "Ratio of Rim/Body diameter"))) %>%
  arrange(variable) %>%
  select(variable, `post-e`, `ch-con`, `D_AD`, `p_value`) %>%
  mutate_at(c("post-e", "ch-con", "D_AD", "p_value"), round, 4)
knitr::kable(kwl_p_cvs_table_post_chi,
             caption = "Coefficient of Variation for metric attributes between European and Chinese presence using Asymptotic test [@Feltz1996]")
```

>>>>

```{r metricCVstest-post-chi, eval=FALSE}
#-----------------------------------CV test for post-e and ch-con pair
kiwulan_pottery_metrics_cvs_plot_cv_test_asym_post_chi <-
  kwl_p_metrics_long_post_chi %>%
  nest(-variable) %>%  # or nest(period, value) %>%
  mutate(asymptotic_test = map(data, # change from mslr_test to asymptotic_test
                               ~bind_cols(asymptotic_test (
                                 .x$value,
                                 .x$period)))) %>%
  unnest(asymptotic_test)
# compute CV
kwl_p_cvs_pre_post <-
  kwl_p_metrics_long_post_chi %>%
  group_by(period, variable) %>%
  summarise(cvs = raster::cv(value, na.rm = TRUE))
# join p-values to CVs
kwl_p_cvs_and_pvalues_post_chi <-
  kwl_p_cvs_pre_post %>%
  left_join(kiwulan_pottery_metrics_cvs_plot_cv_test_asym_post_chi) %>%
  mutate(significant = ifelse(p_value <= 0.05, 'yes', 'no')) %>%
  mutate(variable = factor(variable, ordered = TRUE)) %>%
  arrange(variable)
# making table for CV
kwl_p_cvs_table_post_chi <-
  kwl_p_cvs_and_pvalues_post_chi %>%
  select(-data, -significant) %>%
  pivot_wider(names_from = period, values_from = cvs) %>%
  mutate(variable = factor(variable, levels = c("Rim thickness (mm)",
                                                "Neck thickness (mm)",
                                                "Body thickness (mm)",
                                                "Ratio of Rim/Body thickness",
                                                "Rim diameter (mm)",
                                                "Neck diameter (mm)",
                                                "Body diameter (mm)",
                                                "Ratio of Rim/Body diameter"))) %>%
  arrange(variable) %>%
  select(variable, `post-e`, `ch-con`, `D_AD`, `p_value`) %>%
  mutate_at(c("post-e", "ch-con", "D_AD", "p_value"), round, 4)
knitr::kable(kwl_p_cvs_table_post_chi,
             caption = "Coefficient of Variation for metric attributes between European and Chinese presence using Asymptotic test [@Feltz1996]")

# join two table together
kwl_p_cvs_table_all <-
  kwl_p_cvs_table_pre_post %>% 
  left_join(kwl_p_cvs_table_post_chi, "variable") %>% 
  select(-`post-e.y`) %>% 
  rename(`before European` = "pre-e", `European` = "post-e.x", Chinese = "ch-con",
         `D_AD.1` = "D_AD.x", `D_AD.2` = "D_AD.y",
         `P value.1` = `p_value.x`, `P value.2` = `p_value.y`) %>% 
  select(variable, `before European`, European, Chinese,
         `D_AD.1`, `P value.1`, `D_AD.2`, `P value.2`)
```
